D3064R0: How to Avoid OOTA Without Really Trying

### 2024-02-17 ootavacuous.tex
Update authors and date
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\author{
Paul E.~McKenney\\\email{paulmck@kernel.org} \and
Michael Wong\\\email{fraggamuffin@gmail.com} \and
Maged Michael\\\email{maged.michael@gmail.com} \and
Alan Stern\\\email{stern@rowland.harvard.edu} \and
The Indefatigible TBD
}
\date{January 7, 2024 (Pre-Tokyo)}
\maketitle{}

>>>>

\author{
Paul E.~McKenney\\{\small \email{paulmck@kernel.org}} \and
Alan Stern\\{\small \email{stern@rowland.harvard.edu}} \and
Michael Wong\\{\small \email{fraggamuffin@gmail.com}} \and
Maged Michael\\{\small \email{maged.michael@gmail.com}} \and
The Indefatigible TBD
}
\date{Feburary 16, 2024 (Post-Pre-Tokyo)}
\maketitle{}
